Life in the canopy: community trait assessments reveal substantial functional diversity among fern epiphytes

### 2020-01-14 ms/manuscript.Rmd
Update MS
- Fix pvalue formatting in Table 3
- Use unicode lambda in Table 2

## References
<!-- Insert <div id="refs"></div> to place the refs here instead of at the end -->
<div id="refs"></div>

@@

phylosig_cont_traits %>%
  mutate_at(vars(kval, lambda), ~round_t(., 2)) %>%
  mutate(lambda_pval = format_pval(lambda_pval)) %>%
  mutate(trait = factor(
    trait, 
    levels = c("stipe", "length", "width", "rhizome", 
               "sla", "pinna", "dissection"))) %>%
  mutate(trait = lvls_revalue(
    trait,
    new_levels = c("Stipe length", "Frond length", "Frond width", "Rhizome diam.", 
                   "SLA", "Pinna no.", "Frond dissection"))) %>%
  arrange(trait) %>%
  gt(rowname_col = "trait") %>%
  cols_label(
    kval = md("*K*"),
    k_pval = md("*P*(*K*)"),
    lambda_pval = md("*P*(lambda)"),
    lambda = "lambda"
  )  %>%
  as_latex

@@

phylosig_binary_traits %>%
  mutate(D = round_t(D, 2)) %>%
  mutate(trait = factor(
    trait, 
    levels = c("habit", "gemmae", "glands", "hairs","morphotype"))) %>%
  mutate(trait = lvls_revalue(
    trait,
    new_levels = c("Epiphytic growth", "Gemmae", "Glands", "Hairs", "Cordate morphotype"))) %>%
  arrange(trait) %>%
  gt(rowname_col = "trait") %>%
  cols_label(
    num_present = "Number of presences",
    num_absent = "Number of absences",
    D = md("*D*"),
    prob_random = md("*P*(rnd)"),
    prob_brownian = md("*P*(BM)")
  ) %>% 
  as_latex

>>>>

## References

<!-- FIXME: for some reason, a single space is inserted before each reference when
coverting to docx from tex by pandoc. Remove these from docx file. -->

<!-- FIXME: manually remove "Jr" from inline-citations in docx file. -->

<!-- Insert <div id="refs"></div> to place the refs here instead of at the end -->
<div id="refs"></div>

@@

phylosig_cont_traits %>%
  mutate_at(vars(kval, lambda), ~round_t(., 2)) %>%
  mutate(lambda_pval = format_pval(lambda_pval)) %>%
  mutate(trait = factor(
    trait, 
    levels = c("stipe", "length", "width", "rhizome", 
               "sla", "pinna", "dissection"))) %>%
  mutate(trait = lvls_revalue(
    trait,
    new_levels = c("Stipe length", "Frond length", "Frond width", "Rhizome diam.", 
                   "SLA", "Pinna no.", "Frond dissection"))) %>%
  arrange(trait) %>%
  gt(rowname_col = "trait") %>%
  cols_label(
    kval = md("*K*"),
    k_pval = md("*P*(*K*)"),
    lambda_pval = md("*P*(λ)"),
    lambda = "λ"
  )  %>%
  as_latex

@@

phylosig_binary_traits %>%
  mutate(D = round_t(D, 2)) %>%
  mutate_at(vars(prob_random, prob_brownian), format_pval) %>%
  mutate(trait = factor(
    trait, 
    levels = c("habit", "gemmae", "glands", "hairs","morphotype"))) %>%
  mutate(trait = lvls_revalue(
    trait,
    new_levels = c("Epiphytic growth", "Gemmae", "Glands", "Hairs", "Cordate morphotype"))) %>%
  arrange(trait) %>%
  gt(rowname_col = "trait") %>%
  cols_label(
    num_present = "Number of presences",
    num_absent = "Number of absences",
    D = md("*D*"),
    prob_random = md("*P*(rnd)"),
    prob_brownian = md("*P*(BM)")
  ) %>% 
  as_latex
